Journal Article Summaries

### 2024-08-15 docs/logbook.tex
Cleaned up comments

		Steps to reproduce error:
		\begin{enumerate}
			\item Initialise with 0.1, 0.2, 0.3 and 30°, 25°, -120°. Run the first cell and then second cell, and we should see no deformation of the fitted ellipsoid to a sphere - the parameters remain as 0.479, 0.29,0.0913, 83.83°, 128.2°, 47.02°. The gradients are very close to 0.
			\item Initialise with the parameters 0.479, 0.29,0.0913 and 83.83°, 128.2°, 47.02°. We see that the gradients are non-zero and we optimise to a sphere.
		\end{enumerate}
		a, b, c = 0.4786546028, 0.2901328092,0.09132074619 \\ 
		yaw, pitch, roll = 83.82856741, 128.3492915, 47.0228292

	\end{MeetingMinutes}

>>>>

		Steps to reproduce error:
		\begin{enumerate}
			\item Initialise with 0.1, 0.2, 0.3 and 30°, 25°, -120°. Run the first cell and then second cell, and we should see no deformation of the fitted ellipsoid to a sphere - the parameters remain as 0.479, 0.29,0.0913, 83.83°, 128.2°, 47.02°. The gradients are very close to 0.
			\item Initialise with the parameters 0.479, 0.29,0.0913 and 83.83°, 128.2°, 47.02°. We see that the gradients are non-zero and we optimise to a sphere.
		\end{enumerate}
		a, b, c = 0.4786546028, 0.2901328092,0.09132074619 \\ 
		yaw, pitch, roll = 83.82856741, 128.3492915, 47.0228292
	\end{MeetingMinutes}

	\begin{MeetingMinutes}{Thu 15/08/2024}{u7013004}
		Steve told me that I needed to update the DDN package and it worked!\\
		I spent the past week a bit confused on how to do projection but Steve gave me some clear instructions. I've switched the volume and surface area constraints, but the optimisation is being worse.
	\end{MeetingMinutes}
